\documentclass{ximera}
\input{../preamble.tex}
\title{Derivative}
\begin{abstract}
\end{abstract}
\begin{document}
\maketitle
\begin{dialogue}
\item[Julia] Ah, this sucks!
\item[Dylan] What's up?
\item[Julia] I'm supposed to find the slope of a parabola at a point, and I'm not sure how!
\item[Dylan] Well if we had two points we could make a secant line to approximate it!
\item[Julia] Secant line? What's that?
\item[Dylan] A \textit{secant line} is just a line which connects two points on a function!
\item[Julia] But isn't the \textit{tangent} line one that skims a curve at one point? So the slope of the tangent line is the slope at that point! See?
\[
graph{f(x)=x^2,g(x)=2(x-1)+1}
\]
\item[Dylan] Well do you know how to find the equation for a line with just one point?
\item[Julia]...
\item[James] Come on guys we can approximate the tangent line using the secant line!
\item[Altogether]Let's dive in!
\end{dialogue}



\section{Guided Example}

Consider the function $$f(x) = x^2$$
\[
\graph{f(x)=x^2,g(x)=2(x-1)+1}
\]
%\begin{image}
%\begin{center}
%\begin{tikzpicture}
%\begin{axis}[
%    axis lines = left,
%    xlabel = $x$,
%    ylabel = {$f(x)$},
%]
%Below the red parabola is defined
%\addplot [
%    domain=-10:10, 
%    samples=100, 
%    color=red,
%]
%{x^2};
%\addlegendentry{$x^2$}
%\end{axis}
%\end{tikzpicture}
%\end{center}
%\end{image}

\begin{question}
Find the slope of the secant line between $x = 2$ and $x = 7$.


$\answer{9}$

Does this seem to be a good approximation for slope of the tangent line at $x = 2$?

$\answer{No}$

Dylan thinks we can solve the problem by just picking something closer than 7. Find the slope of the secant line between $x = 2$ and $x = 3$.
$\answer{5}$

Is this a good approximation for the slope of the tangent line at $x=2$?

$\answer{No}$

Is it better than the last attempt?

$\answer{Yes}$
\end{question}
\begin{dialogue}
\item[Julia] Dylan, this still isn't a great approximation...
\item[Dylan] Well, I think we need to get even closer. Like, infinitesimally close! But how would we do that....
\item[James] You guys need some help?
\item[Julia and Dylan] James! How do we find the slope of a line at a point?
\item[James] It isn't too tough! Before, you were considering a certain point as your comparison. What if instead, you used the point you want to evaluate at plus something really small? Let's call it $h$.
\end{dialogue}
\begin{question}
How can you make the $h$ in $$\frac{f(2+h)-f(2)}{(2+h)-2}$$ approach 0?
\begin{hint}
You'll need to use a limit here!
\end{hint}
\begin{freeResponse}
\end{freeResponse}

Using the method you determined, approximate the slope of the tangent line at the point x=2.

$\answer{4}$

\end{question}
\begin{dialogue}
\item[James] Want to know something really cool?
\item[Julia and Dylan] What James?
\item[James] The function we just discovered is how you determine a function's derivative! Using that process, you can find the instantaneous rate of change at any point on a function!
\item[Julia and Dylan] Wow! So cool!
\end{dialogue}

\section{On Your Own}
Using what you've learned, find the derivative of the following functions at the given point.
\setcounter{problem}{0}
\begin{question}
$g(x) = x^2+1$, $x=2$

$\answer{4}$

$h(x) = \frac{1}{x}$, $x=2$

$\answer{-0.25}$

$f(x)=3x^2+4x+2$,$x=-1$

$\answer{-2}$

\item{$f(t)=\sqrt{t^2+1}$,$x=3$}

$\answer{\frac{3}{\sqrt{10}}}$

\item{$f(x) = x+x^{-1}$,$x=4$}

$\answer{3.9375}$

\end{question}

By replacing the point in our formula for the derivative with $x$, we may determine the derivative at any point on the function. Determine the derivative for the following functions.
\begin{question}
$m(x) = x^3$

$\answer{3x^2}$

$n(x) = 3x+2$

$\answer{3}$

$f(x)=4-x^2$

$\answer{-2x}$

$f(x) = 12+7x$

$\answer{7}$

$f(t)=\frac{4}{t+1}$

$\answer{\frac{-4}{(x+1)^2}}$

\end{question}


\section{In Summary}
\begin{dialogue}
\item[Julia] So why is it called a secant line?
\item[James] It comes from the Latin word secare, which means 'to cut'.
\item[Dylan] Ohh, I get it now! Because a secant line is a line that 'cuts' a function!
\end{dialogue}
In this lab we've (hopefully) learned the function for finding a derivative using the limit as $h$ approaches 0. We also learned what secant and tangent lines are. For your convenience, the important definitions are listed below.
\begin{definition}
 A \textbf{secant line} is any line that connects any two points on a curve.
\end{definition}
\begin{definition}
A \textbf{tangent line} is a line which intersects a differentiable curve at a point where the slope of the curve equals the slope of the line.
\end{definition}
\begin{definition}
The \textbf{derivative} $f'(a)$ is defined by the following limit:
$$f'(a)=\displaystyle \lim_{h\rightarrow 0} \frac{f(a+h)-f(a)}{h}$$
\end{definition}
\end{document}